---
title: "linear model from Web"
author: "Yessica Garay"
date: "Spring 2024"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)

```

# Introduction
We will produce three equation models to get  
1. sim score based on arm strenght  
2. sim score based on grip. strength  
3. sim score based on both arm and grip strength  

for each model we will predic sim for arm=88, grip=94

# Methods:
we have numerical responses (sim score) and Numerical explanatory variables (grip and arm strength). so we use numerical~numerical helper file

## Model 1 SIM~ARMS


### scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

There is positive relationship between SIMS and ARMS.if this were perfect linear relationship, all the points would be on a straight line. The correlation between Sim and arm strength is .0

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```
This summarizes the correlation between are strength ans Sim score being around.7


### Inferential  (Build model.1)
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The P value for the coefficient of arm 0.0000000000000002

#### Predict at target point

```{r}
SIMSpredict = predict.lm(model.1, newdata = data.frame(ARM = 88, GRIP = 94))
print(SIMSpredict)
```

The prediction for ARM = 88, and GRIP = 94 is .71

#### scatterplot with model fit


 

## Model 2 SIM~GRIP

### Now add in scatterplot


### Numerical results 


### Inferential  (Build model.2)
  

#### predict model.2 at target point

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
m = data.frame(data['GRIP'],data ['ARM'],data['SIMS'])
cor(m)

```

The table shows that SIMS correlate with GRIP in a positive manner (0.64) and SIMS correlates with ARM also in positive manner,(0.69). This says these variables are useful in predicting SIMS

```{r}
plot(data$GRIP,data$ARM)
```

plot shows grip and arm are do not independent, so this is not necessarily a good model

`
  
### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 = lm(SIMS~GRIP+ARM, data = data)
print(summary.lm(model.3))
```

#### predict model.3 at target point

```{r}
newPoint = data.frame(GRIP=94, ARM=88)
predict.lm(model.3, newPoint, interval = 'prediction')
```

The 95% confidence interval is SIMS is between -2.13 and 2.43. Since this interval contains we do not have a very good prediction for SIMS ## Comparing nested models ANOVA Test
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3

```{r}
anova(model.1,model.3)
```

p-value 0.00000499, this is less than 0.05 so we conclude that model.3 is better than model.1 

### Model.2 vs Model.3

## Informally compare Model.1 with model.2

